% !TEX root = ../main.tex

%************************************************
\chapter{Summary}
\label{ch:summary} 

%************************************************

This thesis has explored relationships between BLR outflows, NLR outflows and hot dust emission. 
This chapter provides a summary of the work presened in the thesis, together with a discussion of future directions for the research. 

The near-infrared band provides a wealth of information on the properties of quasars and their environments at redshifts $2 \lesssim z \lesssim 4$. 
Quasar activity and cosmic star formation both peak during this epoch, and powerful quasar-driven outflows are thought to quench star formation and shut down black hole (BH) accretion. 
We have constructed a large near-infrared spectroscopic catalogue of high redshift quasars to investigate quasar-driven outflows and their relation to fundamental properties of quasars. 

At high redshift, $z \gtrsim 2$, quasar BH masses are derived using the velocity-width of the \ion{C}{IV} broad emission line, based on the assumption that the observed velocity-widths arise from virial-induced motions.  
\ion{C}{IV} has long been known to exhibit significant displacements to the blue and these `blueshifts' almost certainly signal the presence of strong outflows.
As a consequence, single-epoch virial BH mass estimates derived from \ion{C}{IV} velocity-widths are known to be systematically biased compared to masses from the hydrogen Balmer lines.
By combining our near-infrared spectroscopic catalogue (covering the Balmer lines) with optical spectroscopy from SDSS (covering \ion{C}{IV}), we have quantified the bias in \ion{C}{IV} BH masses as a function of the \ion{C}{IV} blueshift. 
\ion{C}{IV} BH masses are shown to be over-estimated by almost an order of magnitude at the most extreme blueshifts.
Using the monotonically increasing relationship between the \ion{C}{IV} blueshift and the mass ratio BH(\ion{C}{IV})/BH(\hans) we derive an empirical correction to all \ion{C}{IV} BH-masses.
The correction depends only on the \ion{C}{IV} line properties and therefore enables the derivation of un-biased virial BH mass estimates for the majority of high-luminosity, high-redshift, spectroscopically confirmed quasars in the literature. 

[\ion{O}{III}] emission probes ionised gas extended over kiloparsec scales in the quasar host galaxies. 
The prevalence of high-velocity blueshifted emission suggests that outflows are very common in luminous quasars at redshifts $z\sim2$. 
There is a strong anti-correlation between the [\ion{O}{III}] EQW and the \ion{C}{IV} blueshift, suggesting that quasar-driven winds are capable of sweeping away gas extended over kilo-parsec scales in the host galaxies. The [\ion{O}{III}] blueshift is correlated with the \ion{C}{IV} blueshift, which could indicate a connection between gas kinematics on sub-parsec and kilo-parsec scales. 
We estimate the kinetic power of the outflows traced by [\ion{O}{III}] to be up to a few percent of the quasar bolometric luminosity, which is similar to the efficiencies required in recent quasar-feedback models. 

Using data from a number of recent wide-field photometric surveys, we build a parametric spectral energy distribution model that is able to reproduce the median optical-infrared colours of tens of thousands of SDSS AGN at redshifts $1 < z < 3$. 
In individual objects, we find significant variation in the near-infrared region dominated by emission from hot dust.   
We find that the hot dust abundance is strongly correlated with the strength of outflows in the quasar BLR and consider the implications of this result in the context of accretion disc wind models.

\section{Future prospects}

Allen \& Hewett will publish improved redshifts for all quasars in the SDSS DR$7$ and DR$12$ catalogues. 
At the same time we will publish catalogues of unbiased BH masses for both SDSS DR$7$ and DR$12$ based on the Allen \& Hewett redshifts. 
The components from the mean-field independent component analysis used in the Allen \& Hewett redshift algorithm will also be published.
With these components, if a rest-frame ultraviolet spectrum is available, it will be straightforward to determine the systemic redshift, via a simple optimisation procedure, and hence calculate the \ion{C}{IV} blueshift. 

Large scatter remains, particularly at low \ion{C}{IV} blueshifts. 
Some of this is correlated with the \ha FWHM, which is in turn correlated with EV1. 
However, no good - need something in the UV spectrum. 
Remarkable we can do so well with a single parameter, but try Blueshift+EQW (e.g. Runnoe)
But better to use data-driven approach (see research proposal stuff). 

Mention John's clustering work. 

Conversely, there are no quasars in our catalogue with \ion{C}{IV} blueshifts $\lesssim0$\,\kms\, and we caution against extrapolating the correction formula to negative blueshifts.
In particular, quasars with negative blueshifts as large as $\sim1000$\,\kms appear in the SDSS DR$7$ catalogue and applying our correction in this regime boosts the derived masses by unphysical factors.    
Need more low blueshift quasars
Hints of tension so then proabbly need a mroe flexbible model

My research has focused on measuring fundamental properties of quasars and quasar-driven outflows in large surveys, with the ultimate goal of understanding the crucial role played by quasars in the evolution of galaxies.
Building on this experience, I plan to (1) use data-driven methods to maximise the information content of spectroscopic survey data, (2) study galaxy-wide outflows traced by narrow [\ion{O}{III}] emission, (3) use integral field unit (IFU) spectroscopy to measure the morphology and energetics of these outflows and their effect on star formation, and (4) use multi-wavelength spectral energy distribution (SED) modelling to study how these outflows are powered.  
My proposed projects, which are summarised below, would mesh effectively with the Galaxy Evolution and SAMI research programs. 

In \citet{coatman17}, I derived a direct empirical correction that maps the \ion{C}{IV} line-width and blueshift (relative to the quasar rest-frame) to the Balmer emission-based black hole (BH) mass. 
I plan to extend this by developing a purely data-driven approach to inferring the BH mass from the rest-frame UV spectrum. 
Allen \& Hewett (in preparation) have run an independent component analysis (ICA) on the SDSS quasar sample that compresses all of the information contained in the UV spectra into a small number of component weights.
Taking the set of 230 objects with NIR spectra (and hence reliable Balmer-based BH masses), I will build a model that learns how these ICA component weights depend on the BH mass. 
After the training step, I can use the model to predict a BH mass (and the associated uncertainty) based only on the ICA component weights for the UV spectrum.
There are numerous algorithms available to tackle this class of supervised learning problem (e.g. random forests). 

Taking this one step further, I will build a data-driven model that predicts the unseen rest-frame optical spectrum from the UV region probed by SDSS spectra at redshifts $z\gtrsim2$.
This approach is inspired by the data-driven model for deriving stellar labels from spectroscopic data developed by \citet{ness15}.
I will use an ICA to generate a set of `labels' describing the optical spectrum. 
I will build a flexible generative model that predicts the flux at each wavelength in the SDSS rest-frame UV spectrum as a function of these weights.
The coefficients in this model, which could be linear or a low-order polynomial, will be trained on the sub-sample of quasars with spectra covering the full optical to UV region. 
Once the coefficents have been determined, I will be able to statistically infer the optical ICA component weights based only on the UV spectrum. 
The optical spectrum can then straightforwardly be reconstructed from the ICA component weights and parameters of interest, such as the BH mass, can be calculated, without the need for follow-up NIR spectroscopy. 
I will also investigate whether an ICA decomposition (or any dimensionality reduction algorithm) can be used to infer the intrinsic quasar luminosity. 
The uncertainty on a single measurement would certainly be large but, with spectra for hundreds of thousands of quasars out to high redshifts, quasars could be used as standard candles to constrain cosmological parameters. 
I am keen to apply similar techniques to other spectroscopic surveys in which CAASTRO researchers are involved. 


\section{Studying feedback with IFU spectroscopy}

Unfortunately, integrated spectra contain little information on the spatial extent or geometry of the outflowing gas.  
To study the morphology and energetics of the outflow, we must turn to spatially-resolved IFU spectroscopy.



Extended outflows have also been detected at high redshifts ($z\gtrsim2$) in a handful of objects \citep[e.g.][]{carniani15}. 

Currently, I am analysing the spatially-resolved kinematics of the ionised gas in the hosts of $\sim$120 luminous quasars at redshifts $z\sim2$ using (mostly archival) SINFONI IFU spectra. 
I have already analysed the spatially-integrated spectra and in many a broad, blueshifted wing in the [\ion{O}{III}] emission is clearly identifiable. 
An ICA on a sample of low-redshift SDSS quasar spectra has been used to generate individual components corresponding to the [\ion{O}{III}] emission originating in static and outflowing gas. 
I can use the relative weights of these two components in each spaxel to generate velocity maps and compare the spatial distributions of the static and outflowing components.
I can then test whether the outflowing component in the [\ion{O}{III}] emission extends to $\sim$kpc scales and
estimate properties of the ionised outflows: the mass outflow rate, momentum rate, and kinetic power.
I will also search for narrow \ha emission associated with star formation, using the relative strength of [\ion{N}{II}] to discriminate between a star formation and AGN origin of the narrow \ha emission \citep{susie16}. 
I will look for anti-correlations in the spatial distributions of outflowing gas and star forming regions, which would be indicative of negative quasar feedback in action.

These observations will be challenging and, given the limited depth of our data, the [\ion{O}{III}] emission is unlikely to be spatially resolved in every object. 
Therefore, I would like to observe a representative sub-set of the large sample presented in Coatman et al. (2017b, in prep.) using SINFONI or KMOS on the VLT. 
Because I have already carefully analysed the [\ion{O}{III}] emission properties of these quasars, it is an ideal sample from which to select targets for IFU spectroscopy. 
One particular goal is to understand the disappearance of the narrow line region in quasars with strong broad line region outflows. 

More careful modelling of \ion{Fe}{II} emission with different tempaltes or cloudy models. 
Recommends instead taking the line ratios in some paper, and broadening the spectra to make a grid. Sherpa allows you to interpolate over the grid of templates in the fit. 




Reverberation mapping of high z quasars
range of civ blueshifts
